A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-23 doc/paper.tex
User study stuff. Fixes #92, fixes #93, fixes #97, fixes #95, fixes #94, fixes #98, fixes #99, fixes #100, fixes #101, fixes #103, fixes #104, fixes #105, fixes #106, fixes #107.

	\subsection{Bad Smells} Fowler's description of code smells
	\cite{fowler2009refactoring} underscored an important point of code quality:
	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum of code
	designs which, by themselves, are not faulty but nevertheless suggest vulnerabilities in code design. 	
	Since then, researchers have applied these concepts to spreadsheet programming, as 
	discussed in section \ref{related-work}. While some of the smells lie beyond the scope
	of the tool, such as those characterizing inter-worksheet connections, others
	have structures which create distinctive features within the tree, leading to
	easy detection through our visualization: \par

@@

	\subsection{Use in Smell Tracking}
	\begin{wrapfigure}{O}{.25\textwidth} \centering \includegraphics{SUM}
		\label{fig:sum} \caption{An abundance of parameters in SUM} \end{wrapfigure}

	The discovery of errors and bad design, whether by purpose or accident,
	produced the more jarring events of the study, and as such, most users
	commented on the tool's ability to locate these problems in spreadsheet design.
	This was often supported by the distinctive visual signatures of certain bad
	practices: multiple arguments produce towers of nodes, deep function nesting
	stretches the tree horizontally, and so on. As such, the participants remarked
	on the problems quickly after opening: P3, exploring the example for a
	27-argument SUM (with SUM's initial appearance pictured left), diagnosed the
	situation with either incompetency or just plain weirdness; P2, meanwhile,
	decided that the spreadsheet's author "was having a bad day" when writing an
	AVERAGE with 18 distinct arguments. Aside from these implicit cues, there are
	also nodes which refer to formula errors, prefixed with \#s, which P4 said
	could be useful if marked well. Furthermore, once these errors are found, the
	participants could then open the offending spreadsheets, discovering that, even
	in context, some of these formulae remained incomprehensible, posing problems
	for the spreadsheet transfer scenarios as outlined by Hermans
	\cite{hermans2011supporting}. The tool, then, aggregates these issues in a
	single place, accessible to either the unguided user and the ones who know
	exactly where to find these issues. \par

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could suffice just as well for that purpose. However, they also remarked
	that this visual interface better supports the case when searching for new and
	unknown brands of bad smell.

	Because the exploratory design makes no qualitative judgment and visualizes
	benign designs with the problematic, it therefore allows for flexible
	interpretation of what is an issue; that is, a user might not realize a certain
	design is suboptimal until they see it in the tree and, at the point, find
	every instance of it.

>>>>

	\subsection{Bad Smells} \label{badsmells} Fowler's description of code smells
	\cite{fowler2009refactoring} underscored an important point of code quality:
	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum of code
	designs which, by themselves, are not faulty but nevertheless suggest vulnerabilities in code design. 	
	Since then, researchers have applied these concepts to spreadsheet programming, as 
	discussed in section \ref{related-work}. While some of the smells lie beyond the scope
	of the tool, such as those characterizing inter-worksheet connections, others
	have structures which create distinctive features within the tree, leading to
	easy detection through our visualization: \par

@@

	\subsection{Use in Smell Tracking}
	\begin{wrapfigure}{O}{.25\textwidth} \centering \includegraphics{SUM}
		\label{fig:sum} \caption{An abundance of parameters in SUM. Encountering this, P4
			remarked, "Woah."} \end{wrapfigure}

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just some that's weird." Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree where they are found, 
	which P4 said could be useful for tracking these problems if marked well.

	Additionally, because the files in the Enron set had name with the author
	as a prefix, P2 commented that they could use the tool in a company
	setting to follow up with repeat offenders. For instance, they first
	encountered a particular author's name when investigating an AVERAGE function
	with 18 distinct arguments for which our participant could not discern any
	logical order, even after opening the source spreadsheet; the same name
	popped up again as P2 looked at a RATE function relying on several hard-coded
	values. P2 said that, if they were a manager or project leader, this recurrence
	was a sign to talk to the author personally and figure out why
	these problems were there, as to prevent more in the future. They also added
	that these problems would grow worse if this particular author left the company
	and no one remained who understood these formulae, a concern that aligns with
	Hermans' transfer scenarios \cite{hermans2011supporting}.

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could suffice just as well for that purpose. However, they also remarked
	that this visual interface better supports the case when searching for new and
	unknown brands of bad smell. Because the exploratory design makes no
	qualitative judgment and visualizes benign designs with the problematic, it
	therefore allows for flexible interpretation of what is a smell; that is, a
	user might not realize a certain design is suboptimal until they see it in the
	tree and, at the point, find specific examples of where it occurs in the
	spreadsheets.
